\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-05-11 paper.tex
expressed seq in terms of bind
introduced satisfy combinator using bind

    From the above example, it can be deduced that the outcome of the first parser can be sequentially consumed by the second parser and so on if other parsers are included. Hence, the \textit{bind} infix operator will dodge the complication introduced by the nested tuples.

>>>>

    From the above example, it can be deduced that the outcome of the first parser can be sequentially consumed by the second parser and so on if other parsers are included. Hence, the \textit{bind} infix operator will dodge the complication introduced by the nested tuples. Consequently, the \textit{seq} can be defined using the \textit{bind} operator:

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell]
      p `seq` q = p `bind` \x -> q `bind` \y -> result (x, y)
    \end{lstlisting}
    \end{tcolorbox}

    Unfortunately, the modified \textit{seq} operator will not work in practice. (Why? ask Peter) \\ \\ 
    The monadic \textit{bind} operator can be used to define parsers of a different nature. For example, a \textbf{satisfy} combinator may be constructed as a function that takes a predicate as input and returns a parser that consumes the first element of a string if the predicate is true and fails if the predicate is false. In order to fulfill the required parsing behavior, the primitive parsers \textit{oneItem} and \textit{zero} mentioned in section 5.2 are necessary.
